Properties and Bayes fitting of restricted Boltzmann machines

### 2017-06-13 writing/draft.Rmd
stupid cross-ref

cbind(tbl[1:8,], tbl[9:16,], tbl[17:24,]) %>%
  xtable(label = "tab:theta", 
         caption = "Parameters used to fit a test case with $V = H = 4$. This parameter vector was chosen as a sampled value of $\\boldsymbol \\theta$ that was not near the convex hull of the sufficient statistics for a grid point in Figure \\ref{fig:degen-plots} with $< 5$\\% near-degeneracy.", align = c("l", rep(c("r", "r"), times = 3))) %>%
  print(sanitize.text.function=function(x){x}, include.rownames = FALSE, comment = FALSE)

>>>>

cbind(tbl[1:8,], tbl[9:16,], tbl[17:24,]) %>%
  xtable(label = "tab:theta", 
         caption = "Parameters used to fit a test case with $V = H = 4$. This parameter vector was chosen as a sampled value of $\\boldsymbol \\theta$ that was not near the convex hull of the sufficient statistics for a grid point in Figure \\ref{fig:degen_plots} with $< 5$\\% near-degeneracy.", align = c("l", rep(c("r", "r"), times = 3))) %>%
  print(sanitize.text.function=function(x){x}, include.rownames = FALSE, comment = FALSE)
